### 2023-10-27 conclusions/conclusion.tex
Finished this part

\subsection{onChip area}

The \ac{LSTM} and \ac{GRU} blocks's onChip area is impossible to estimate, as part of the circuit is made of verilog-A models. However, to get a general idea of the area of the chip, it can be assumed that the area of the circuit mainly depends on the the area of a memrisor. Since the number of memristors is the number of weights in the circuit, the minimum area of any \ac{NN} can be determined.

@@

The feature size represents the length of the side of the chip is the chip was manufactured in a square.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \rowcolor{gray}
    Model & Parameters & Minimum area & Approximate feature size \\
    \hline
    Airline \ac{GRU} $n_h=4$ & $77$ & $693\mu m^2$ & $26.3\mu m$\\
    \hline
    Airline \ac{LSTM} $n_h=4$ & $101$ & $909\mu m^2$ & $30.1\mu m$\\
    \hline
    \ac{C. elegans} \ac{GRU} $n_h=8$ & $348$ & $3132\mu m^2$ & $56.0\mu m$\\
    \hline
    \ac{C. elegans} \ac{LSTM} $n_h=8$ & $452$ & $4068\mu m^2$ & $63.8\mu m$\\
    \hline
    \multirow{3}{*}{\acs{LLaMA}-2} & $7\cdot 10^9$ & $630 cm^2$ & $25.1 cm$ \\
    \cline{2-4}
    & $13\cdot 10^9$ & $1170 cm^2$ & $34.2 cm$ \\
    \cline{2-4}
    & $70\cdot 10^9$ & $6300 cm^2$ & $79.4 cm$ \\
    \hline
    \acs{GPT}-3 & $175\cdot 10^9$ & $1.57 m^2$ & $1.25m$\\
    \hline
    \acs{GPT}-4 & $1\cdot 10^{12}$ & $9.00 m^2$ & $3m$\\
    \hline
  \end{tabular}
  \caption{Estimated onChip areas}
  \label{tab:areas}
\end{table}

Nevertheless, it is interresting to look at those approximation.

>>>>

\subsection{onChip area}\label{subsec:area}

The \ac{LSTM} and \ac{GRU} blocks's onChip area is impossible to estimate, as part of the circuit is made of verilog-A models. However, to get a general idea of the area of the chip, it can be assumed that the area of the circuit mainly depends on the the area of a memrisor, because the area of a memristor is much greater than the ones of the other components. Since the number of memristors is the number of weights in the circuit, the minimum area of any \ac{NN} can be determined. The area for a memristor was determined using the feature size of the memristors that can be fabricated at \ac{INESC}. The typical memristor that can be fabricated at \ac{INESC} is $3\mu m$, which would make the approximate area for a memristor $A_{memristor}=9\mu m^2=9\cdot 10^{-12} m^2$

@@

The feature size represents the length of the side of the chip if the chip was manufactured in a square.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \rowcolor{gray}
    Model & Parameters & Minimum area & Approximate feature size \\
    \hline
    Airline \ac{GRU} $n_h=4$ & $77$ & $693\mu m^2$ & $26.3\mu m$\\
    \hline
    Airline \ac{LSTM} $n_h=4$ & $101$ & $909\mu m^2$ & $30.1\mu m$\\
    \hline
    \ac{C. elegans} \ac{GRU} $n_h=8$ & $348$ & $3132\mu m^2$ & $56.0\mu m$\\
    \hline
    \ac{C. elegans} \ac{LSTM} $n_h=8$ & $452$ & $4068\mu m^2$ & $63.8\mu m$\\
    \hline
    \multirow{3}{*}{\acs{LLaMA}-2} & $7\cdot 10^9$ & $630 cm^2$ & $25.1 cm$ \\
    \cline{2-4}
    & $13\cdot 10^9$ & $1170 cm^2$ & $34.2 cm$ \\
    \cline{2-4}
    & $70\cdot 10^9$ & $6300 cm^2$ & $79.4 cm$ \\
    \hline
    \acs{GPT}-3 & $175\cdot 10^9$ & $1.57 m^2$ & $1.25m$\\
    \hline
    \acs{GPT}-4 & $1\cdot 10^{12}$ & $9.00 m^2$ & $3m$\\
    \hline
  \end{tabular}
  \caption{Estimated onChip area for different models of \acp{NN}}
  \label{tab:areas}
\end{table}

Nevertheless, it is interresting to look at those approximation. It shows that the simple models used in this work would take a very small onChip area, even though this a very raw number. It also shows the current limit with state of the art \acp{NN} at the current time.
